Storm surges in the Strait of Georgia simulated with a regional model

### 2015-04-28 AO_guides/manuscriptAO.tex
Modifed weather figure caption

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{Comparison of observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson (upper) and Sandheads (lower). Observed winds shown in solid black, low resolution CGRF model in dashed black and high resolution model in grey. Observations are from the Environment Canada Climate Data archives \citep{ECClimateArchive}.}
\label{fig:dec2012_weather}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{Comparison of observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson (upper) and Sandheads (lower). Observed winds shown in solid black, low resolution CGRF model in dashed black and high resolution model in grey. Observations {\color{red} from Sandheads and Point Atkinson} \are from the Environment Canada Climate Data archives \citep{ECClimateArchive}. {\color{red} Observations at the NOAA Buoy are found at this url: http://www.ndbc.noaa.gov/station_page.php?station=46087. Wind direction represents the direction that the wind is headed.} }
\label{fig:dec2012_weather}
\end{figure}
